---
title: "Creation of the interpolation Grid"
author: "Thomas Goossens"
date: "11/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all()
library(dplyr)
library(sf)
```

```{r spatializeconfig, include=FALSE}
# trick to avoir overwriting error with st_write - https://github.com/r-spatial/sf/issues/274
files = list.files()
if (!is.null("incagridExplVars.geojson" %in% files)) {
  file.remove("incagridExplVars.geojson")
}
```

## Introduction

The produced dataset will be injected into the postgres DB.
The incagrid for Wallonia has been built from data provided by RMI. 
Like all the other datasets of the package, the code used to generate the grid is available under ./data-raw

## loading the grid points 
```{r load-grid}
# this is generated in data-raw/makeData.R and uses raw data provided by RMI
data(grid.sf)
grid.sf = grid.sf["px"]
head(grid.sf)
```

We see that this `grid.sf` dataset contains the RMI `px` reference and the location of the grid points stored in the geometry attribute.

We will now inject the static explanatory variables `aspect`, `slope` and `elevation`

## adding explanatory variables to the grid

The explanatory static variabels are stored into the `grid.df` dataset. It also contains the `px` attribute that will allow us to make the join with the `grid.sf` object.

```{r join-explanatory}
# loading the explanatroy var dataset
data("grid.df")
# removing X and Y cols
grid.df = grid.df %>%
  dplyr::select(1:4)
# excerpt of the data 
head(grid.df)
# joining to grid.sf
grid.sf = grid.sf %>%
  dplyr::left_join(grid.df, by = "px")
# excerpt of the data 
head(grid.sf)
```

## Writing to file

We can now write our spatial object that contains the explanatory variables to a geojson file.

```{r write to file}
# transforming to proj EPSG = 4326 (geojson standard)
grid.sf = sf::st_transform(grid.sf, 4326)
sf::st_write(obj = grid.sf, dsn = "incagridExplVars.geojson")
```

You can download this geojson file [here](https://github.com/pokyah/agrometeoR/blob/master/vignettes/incagridExplVars.geojson)
